|

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Update figures Rmarkdown and PDF

# draw table 1
knitr::kable(marker_longlist2[ ,-9],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1,2, 6,7, 13:15, 18:23, 27, 32, 38:40, 42:45), 
           underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 23) %>% 
  pack_rows("Cell wall, cell surface", 24, 36) %>% 
  pack_rows("Endoplasmic reticulum", 37, 41) %>% 
  pack_rows("Endosome, Golgi, transport vesicle", 42, 44) %>% 
  pack_rows("Vacuole", 45, 45) %>% 
  pack_rows("Mitochondrion", 46, 47) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} homolog as 
                         annotated in the Candida Genome Database (48, 49).", 
                        "Protein localisation was obtained from the GO Cellular
                        Component annotation in the \\\\textit{C. albicans} 
                        UniProt reference proteome UP000000559 (58).", 
                        "Presence of transmembrane domains and absence of a 
                        signal peptide was predicted using TOPCONS2 (59).",
                        "The name Evp1 for the protein encoded by orf19.6741 
                        was proposed in the present study."), 
           escape = FALSE, 
           threeparttable = TRUE)
```

@@

f1c <- nta_total %>% 
  ggboxplot(x = "Strain", y = "part_per_prot", 
            color = "Strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15,
            ylab = expression("Particles /"~paste(mu,g)~"protein"))
f1c <- ggpar(f1c, 
             yscale = "log10", 
             format.scale = TRUE, 
             ylim = c(8e8, 8e10),
             font.y = 10, 
             legend = "none") + 
  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
                     y.position = c(10.45, 10.65, 10.85), 
                     tip.length = 1e-2, 
                     label.size = 3) + 
  theme(axis.title.x = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
                             unit = "inches")) + 
  scale_x_discrete(labels = c("ATCC90028" = "A9", 
                              "ATCC10231" = "A1", 
                              "Biofilm" = "B", 
                              "DAY286" = "Y"))
```

```{r figure1, fig.width=7.1, fig.height=4}
# draw figure 1
ggarrange(f1a, 
          ggarrange(f1b, f1c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))
```

@@

# generate volcano plot
f2b4 <- plot_volcano(data = biofilm_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     use_labels = TRUE, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig")) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('105')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('100')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('453')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure2, fig.width=7.1, fig.height=6}
# draw figure 2
ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f2b1, f2b2,
                    f2b3, f2b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))
```

@@

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4,6, 31,33:35,45, 49:52), f3_pal) + 
  annotate("text", x = 14, y = 70, label = "bold('ATCC10231')", parse = TRUE)
```

```{r figure3, fig.width=7.2, fig.height=6}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")
```

@@

# figure 4d MDS [dim3, dim2]
f4d <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(3,2)) + 
  scale_x_continuous(limits = c(-1.5, 2), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-2, 1.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical", 
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0.1), 
        legend.box.margin = margin(t = -10, r = -6, b = -10, l = -10)) + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 3") + 
  ylab(label = "Dimension 2")
```

```{r figure4, fig.width=7.1, fig.height=5}
ggarrange(ggarrange(f4a, f4b,
                    labels = c("A", "B"),
                    ncol = 2,
                    nrow = 1),
          ggarrange(f4c, f4d,
                    labels = c("C", "D"),
                    ncol = 2,
                    nrow = 1, 
                    common.legend = TRUE,
                    legend = "right", 
                    align = "hv"),
          labels = NULL,
          ncol = 1,
          nrow = 2,
          heights = c(2, 3))
```

@@

f5_go8 <- process_fungifun("figures/f5_GO_clust8.csv")
```

```{r figure5, fig.height=6}
f5 <- png::readPNG("figures/figure5.png")

@@

f6b <- as_ggplot(f6b_venn) + 
  theme(plot.margin = unit(c(1.2,0,0,0), "lines"))
```

```{r figure6, fig.width=2.5, fig.height=4}
ggarrange(f6a, f6b, 
          labels = c("A", "B"), 
          ncol = 1,
          nrow = 2)
```

@@

```{r figure7, fig.width=4, fig.height=3.6}
f7 <- png::readPNG("figures/figure7.png")

ggplot() + 
  background_image(f7)
```

@@

```{r figure8, fig.width=7.2, fig.height=6}
f8 <- png::readPNG("figures/figure8.png")

>>>>

# draw table 1
tab1 <- knitr::kable(marker_longlist2[ ,-9],
                     caption = tab1_cap, 
                     format = "latex", 
                     booktabs = TRUE, 
                     longtable = TRUE, 
                     linesep = "", 
                     escape = FALSE)  %>% 
  row_spec(row = c(1,2, 6,7, 13:15, 18:23, 27, 32, 38:40, 42:45), 
           underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 23) %>% 
  pack_rows("Cell wall, cell surface", 24, 36) %>% 
  pack_rows("Endoplasmic reticulum", 37, 41) %>% 
  pack_rows("Endosome, Golgi, transport vesicle", 42, 44) %>% 
  pack_rows("Vacuole", 45, 45) %>% 
  pack_rows("Mitochondrion", 46, 47) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} homolog as 
                         annotated in the Candida Genome Database (48, 49).", 
                        "Protein localisation was obtained from the GO Cellular
                        Component annotation in the \\\\textit{C. albicans} 
                        UniProt reference proteome UP000000559 (58).", 
                        "Presence of transmembrane domains and absence of a 
                        signal peptide was predicted using TOPCONS2 (59).",
                        "The name Evp1 for the protein encoded by orf19.6741 
                        was proposed in the present study."), 
           escape = FALSE, 
           threeparttable = TRUE)

# export table 1 LaTeX code with \\ line endings removed in a text file
tab1_clean <- gsub("\\\\\\\\\n", "\n", tab1)

cat(tab1_clean, file = "tables/table_1.txt", sep = "\n")

# show table 1 in PDF output
tab1
```

@@

f1c <- nta_total %>% 
  ggboxplot(x = "Strain", y = "part_per_prot", 
            color = "Strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15,
            ylab = expression("Particles /"~paste(mu,g)~"protein"))
f1c <- ggpar(f1c, 
             yscale = "log10", 
             format.scale = TRUE, 
             ylim = c(8e8, 8e10),
             font.y = 10, 
             legend = "none") + 
  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
                     y.position = c(10.45, 10.65, 10.85), 
                     tip.length = 1e-2, 
                     label.size = 3) + 
  theme(axis.title.x = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
                             unit = "inches")) + 
  scale_x_discrete(labels = c("ATCC90028" = "A9", 
                              "ATCC10231" = "A1", 
                              "Biofilm" = "B", 
                              "DAY286" = "Y"))

# arguments for figure 1 export
f1_args <- list(tiff = list(type = "cairo"))
```

```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
# draw figure 1
ggarrange(f1a, 
          ggarrange(f1b, f1c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))
```

@@

# generate volcano plot
f2b4 <- plot_volcano(data = biofilm_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     use_labels = TRUE, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig")) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('105')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('100')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('453')", 
           parse = TRUE, colour = unname(ev_pal[1]))

# arguments for figure 2 export
f2_args <- list(tiff = list(type = "cairo"))
```

```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
# draw figure 2
ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f2b1, f2b2,
                    f2b3, f2b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))
```

@@

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4,6, 31,33:35,45, 49:52), f3_pal) + 
  annotate("text", x = 14, y = 70, label = "bold('ATCC10231')", parse = TRUE)

# arguments for figure 3 export
f3_args <- list(tiff = list(type = "cairo"))
```

```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")
```

@@

# figure 4d MDS [dim3, dim2]
f4d <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(3,2)) + 
  scale_x_continuous(limits = c(-1.5, 2), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-2, 1.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical", 
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0.1), 
        legend.box.margin = margin(t = -10, r = -6, b = -10, l = -10)) + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 3") + 
  ylab(label = "Dimension 2")

# arguments for figure 4 export
f4_args <- list(tiff = list(type = "cairo"))
```

```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
ggarrange(ggarrange(f4a, f4b,
                    labels = c("A", "B"),
                    ncol = 2,
                    nrow = 1),
          ggarrange(f4c, f4d,
                    labels = c("C", "D"),
                    ncol = 2,
                    nrow = 1, 
                    common.legend = TRUE,
                    legend = "right", 
                    align = "hv"),
          labels = NULL,
          ncol = 1,
          nrow = 2,
          heights = c(2, 3))
```

@@

f5_go8 <- process_fungifun("figures/f5_GO_clust8.csv")

# arguments for figure 5 export
f5_args <- list(tiff = list(type = "cairo"))
```

```{r figure5, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f5_args, dpi=600}
f5 <- png::readPNG("figures/figure5.png")

@@

f6b <- as_ggplot(f6b_venn) + 
  theme(plot.margin = unit(c(1.2,0,0,0), "lines"))

# arguments for figure 6 export
f6_args <- list(tiff = list(type = "cairo"))
```

```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
ggarrange(f6a, f6b, 
          labels = c("A", "B"), 
          ncol = 1,
          nrow = 2)

# arguments for figure 7 export
f7_args <- list(tiff = list(type = "cairo"))
```

@@

```{r figure7, fig.width=4, fig.height=3.6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f7_args, dpi=600}
f7 <- png::readPNG("figures/figure7.png")

ggplot() + 
  background_image(f7)

# arguments for figure 8 export
f8_args <- list(tiff = list(type = "cairo"))
```

@@

```{r figure8, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f8_args, dpi=600}
f8 <- png::readPNG("figures/figure8.png")

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Update figures Rmarkdown and PDF

# extract DE results
# adj.p.val cutoff is 0.01, log2FC cutoff is 1
a9_res <- get_results(efit = a9_efit,
                      mat = a9_de,
                      p_val = 0.01,
                      lfc = 1,
                      type = "individual")[[1]]
```

@@

```{r figureS1, fig.cap=fs1_cap, fig.width=5.45, fig.height=6}
# construct figure 1
fs1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           seperate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

fs1 <- png::readPNG("figures/figures1.png")

# draw figure S1
ggplot() + 
  background_image(fs1)
```

```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript')}
fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
              determined by nanoparticle tracking analysis (NTA).} A line plot 
              for each EV biological replicate from each strain is shown. Each 
              line plots represents the average of three technical replicates 
              and the dashed grey lines indicate 100 nm.")

>>>>

# extract DE results
# adj.p.val cutoff is 0.01, log2FC cutoff is 1
a9_res <- get_results(efit = a9_efit,
                      mat = a9_de,
                      p_val = 0.01,
                      lfc = 1,
                      type = "individual")[[1]]

# arguments for figure S1 export
fS1_args <- list(tiff = list(type = "cairo"))
```

@@

```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=fS1_args, dpi=600}
# construct figure 1
fS1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           seperate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

fS1 <- png::readPNG("figures/figures1.png")

# draw figure S1
ggplot() + 
  background_image(fS1)

# arguments for figure S2 export
fS2_args <- list(tiff = list(type = "cairo"))
```

```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
              determined by nanoparticle tracking analysis (NTA).} A line plot 
              for each EV biological replicate from each strain is shown. Each 
              line plots represents the average of three technical replicates 
              and the dashed grey lines indicate 100 nm.")
